Using VDMS to Index and Search 100M Images

### 2020-03-30 yfcc100m/paper/vldb2020/design.tex

\textbf{VDMS API:}
VDMS API is easy to use and explicitly pre-defines certain
visual primitives associated with metadata, images, videos, and feature vectors.
While we use a graph database to store our metadata,
the API is not graph-specific.
Authors have paid particular attention to hide the complexities of our internal
implementation and up-level the API to a JSON-based
API\footnote{https://github.com/IntelLabs/vdms/wiki/API-Description},
which is very popular across various application domains.
By defining a new JSON-based API, there is a trade-off between
expressiveness (compared to SPARQL or Gremlim, or even SQL) and
the ability to natively support visual data operations.
However, it should be possible to achieve similar levels of
expressiveness compared to more mature query languages over time.
The current front-ends available are a Python and C++ client
library to provide a simple query function that accepts a JSON string with
commands and an array (or vector) of blobs.

>>>>

\textbf{VDMS API:}
VDMS API is easy to use and explicitly pre-defines certain
visual primitives associated with metadata, images, videos, and feature vectors.
While we use a graph database to store our metadata,
the API is not graph-specific.
Authors have paid particular attention to hide the complexities of our internal
implementation and up-level the API to a JSON-based
API\footnote{https://github.com/IntelLabs/vdms/wiki/API-Description},
which is very popular across various application domains.
By defining a new JSON-based API, there is a trade-off between
expressiveness (compared to SPARQL, Gremlim, or even SQL) and
the ability to natively support visual data operations.
However, it should be possible to achieve similar levels of
expressiveness compared to more mature query languages over time.
The current front-ends available are a Python and C++ client
library to provide a simple query function that accepts a JSON string with
commands and an array (or vector) of blobs.
